Carcinoma

### 2022-07-04 inst/carcinoma.Rmd

Here, the object of inference is the set of pathologists.  Informative

The probability model is as follows.  To each pathologist $i,1\leq i
\leq 7$, we assign a non-negative Bradley-Terry strength and require
$\sum p_i=1$.  Given that two pathologists $i$ and $j$ differ in their
diagnosis then the probability of $i$ diagnosing the presence, and $j$
diagnosing the absence, of carcinoma is given by

@@

(here superscripts $+$ and $-$ refer to a positive and negative
diagnosis respectively).  Operationally the way we implement this in
`hyper2` idiom is to posit an (unobservable) ranking on the
clinicians: we place the clinicians in order from most convinced of
the presence of carcinoma to the least convinced.  Thus a ranking of
`DACBEGF` means that clinician `D` was most convinced of the presense
of carcinoma and `F` least convinced.  Given this, and given a single
slide, our actual observation might be that `D` and `A` diagnosed
presence, and the others diagosed absence, of carcinoma.  The
corresponding entry would be

>>>>

Here, the object of inference is the set of pathologists.  The
probability model is as follows.  To each pathologist $i,1\leq i \leq
7$, we assign a non-negative Bradley-Terry strength and require $\sum
p_i=1$.  Given that two pathologists $i$ and $j$ differ in their
diagnosis then the probability of $i$ diagnosing the presence, and $j$
diagnosing the absence, of carcinoma is given by

@@

(here superscripts $+$ and $-$ refer to a positive and negative
diagnosis respectively).  Operationally the way we implement this in
`hyper2` idiom is to posit an (unobservable) ranking on the
clinicians: we place the clinicians in order from most convinced of
the presence of carcinoma to the least convinced.  Thus a ranking of
`DACBEGF` means that clinician `D` was most convinced of the presence
of carcinoma and `F` least convinced.  Given this, and given a single
slide, our actual observation might be that `D` and `A` diagnosed
presence, and the others diagnosed absence, of carcinoma.  The
corresponding entry would be
